
\newcommand{\ARMY}

\begin{rubric}{Employment History} 
  \entry*[2024 - now ] 
  \textbf{T.A. Quantum Infromation Lecturer.} \par  
  \emph{ Taking part in constructing a new course at the Hebrew University, including writing recitations and exercises from scratch. }     
  \entry*[2022 - 2024 ] 
  \textbf{T.A. Data Structures Lecturer.} \par  
  \emph{Teaching the data structures course. At the Hebrew University, the course is considered as the first theoretical course in computer science. Apart from teaching, the role also requires writing the exam and the exercises.}     
  \entry*[2024] 
  \textbf{IBM Quantum. PhD Student Intern.} \par  
  \emph{Been responsible for 'protobufing' the quantum circuits sent to be executed on the quantum hardware. In addition, taking part in integrating known error mitigation solutions into IBM flow.}     
  \entry*[2020]% 
  \textbf{Algorithm Developer, Mobileye.}\par 
  \emph{In the Dynamic Road Experience Management department, which develops a (part of) map of temporary changes such as construction sites, potholes, and traffic jams. The map designd to serve the autonomas viecheles.} 
    % My role touches the entire flow from recognizing an anomaly and managing the memory in the real-time environment (competitive with more than a hundred other threads that      } 
  \entry*[2015 -- 2018]% 
  \textbf{Soldier, Sergeant, Platoon Sergeant.}  
  \ifdefined\ARMY
\emph{Serving in Infantry (In Israel, There is a duty service of three years). I had the right to lead a class. I am proud to say that my lieutenant, while I was rocky, was also the platoon deputy commander when I was a rocky sergeant and my platoon commander during my term as a platoon sergeant. Which points out that people are choosing to rework with me. } 
\fi
  \entry*[2014 - 2015]% 
  \textbf{Backend Developer, AOL Israel (AOL Vidoible).}\par 
  \emph{My team at AOL Israel was responsible for embedding a purchased startup. That includes re-encoding videos of the legacy version into a new one. I was still a high student at that time, and my term there lasted till my recruiting day. }  
\end{rubric}
