%\newcommand{\ARMY}
\begin{rubric}{Miscellaneous Experience}

\subrubric{Awards and Achievements}
\entry*[2012 -- 2014] \textbf{Mathematical and Programming Competition Participation (without winning)} \emph{I regularly participated at the national math olympiad (Gilis), Grossman olympiad, Tournament of the Towns, Code-Guro, Skillz (8200 competition) and more, most of the times I didn't win any prize. The achievements are listed in the following bullets.}
\entry*[2014] \textbf{Tournament of the Towns.} \emph{Extreamly hard math contest - commendable grade.}
\entry*[2014] \textbf{Computer Science National Olympiad.} \emph{I got into stage C, preparation for the top 30 high school students, to the international contest. And during that stage, I was ranked among the top ten competitors.}
\ifdefined\ARMY
\entry*[2017] \textbf{First Place Platoons Competition.} \emph{As a rocky platoon sergeant my platoon won(by far) the Bootcamp contest by taking five out nine competition.}     
\entry*[2018] \textbf{Combat Service Scholarship.}  
\fi
\entry*[2018] \textbf{Dean Prize and Scholarship for Outstanding Student Performance.} \emph{During my first year, I won the dean's prize award. It's also worth mentioning that in that year, I accumulated 70 right points (the standard program requires roughly 40 points), Including all the obligatory theoretical computer science courses. }
\entry*[2022] \textbf{Master Outstanding Schoolership and Founding.} \emph{I completly founded by the faculity.} 
\entry*[2022] \textbf{Classiq Competition.} \emph{I participated in Classiq computation, in which the task was to write a circuit that simulates a given Hamiltonian at a certain accuracy and minimal depth. } 
\end{rubric}


